%----------------------------------------------------------------------------------------
% packages and other configurations
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv}

\title{Curriculum vitae}
\date{2025\\ April}
\author{Luca Zulian}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
% title and contact information
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.32\textwidth}
    \vspace{-\baselineskip}

    \colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{ Luca }}}}}
    \colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{ Zulian }}}}}

    \vspace{0.3cm}
    {\large\textbf{Senior Backend Engineer}}
    \vspace{0.2cm}
\end{minipage}
\begin{minipage}[t]{0.370\textwidth}
    \vspace{-\baselineskip}

    \hfill
\end{minipage}
\begin{minipage}[t]{0.370\textwidth}
    \vspace{-\baselineskip}

    \icon{Phone}{12}{+39 347 529 4448}\\
    \icon{MapMarker}{12}{Milan, Italy}\\
    \icon{At}{12}{\href{mailto:info@lucazulian.it}{info@lucazulian.it}}\\
    \icon{Linkedin}{12}{\href{https://www.linkedin.com/in/zulianluca}{linkedin.com/in/zulianluca}}\\
    \icon{Github}{12}{\href{https://github.com/lucazulian}{github.com/lucazulian}}\\
\end{minipage}

%----------------------------------------------------------------------------------------
% professional summary
%----------------------------------------------------------------------------------------

\cvsect{Professional Summary}

\begin{minipage}[t]{1.0\textwidth}
    \vspace{-\baselineskip}
    Senior Backend Engineer with 20+ years of experience designing and delivering scalable, high-availability distributed systems and backend services. Deep expertise in functional programming with hands-on experience in Elixir, Rust, Python, Haskell, and more. Specialised in microservices architecture, event-driven systems (CQRS/Event Sourcing), real-time data pipelines, and cloud-native infrastructure on AWS. Experienced in integrating AI and large language models (LLMs) into production applications. Strong advocate for open-source software, CI/CD, observability, and engineering best practices including continuous delivery, defensive programming, and automated testing. Passionate about compilers, interpreters, domain-specific languages (DSLs), virtual machines, and autonomous systems.
\end{minipage}

%----------------------------------------------------------------------------------------
% technical skills
%----------------------------------------------------------------------------------------

\cvsect{Technical Skills}

\begin{minipage}[t]{1.0\textwidth}
    \vspace{-\baselineskip}
    \textbf{Programming Languages:} Elixir, Rust, Python, Haskell, TypeScript, Java, C, C\#, OCaml, Erlang, Scheme\\
    \textbf{Frameworks \& Libraries:} Phoenix, Ecto, Commanded, ASP.NET, Node.js, Xamarin\\
    \textbf{Cloud \& Infrastructure:} AWS, Terraform, Docker\\
    \textbf{Databases \& Messaging:} PostgreSQL, MongoDB, RabbitMQ\\
    \textbf{Methodologies:} Microservices, CQRS, Event Sourcing, Domain-Driven Design (DDD), Test-Driven Development (TDD), CI/CD, A/B Testing, Observability\\
    \textbf{AI \& Machine Learning:} LLM Integration, AI-powered feature development\\
\end{minipage}

%----------------------------------------------------------------------------------------
% experience
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
    \entry{06/2024 \newline Present\\\footnotesize{full remote}}
        {Senior Backend Engineer}
        {Sibill \textnormal{(FinTech)}}
        {Contributed to automating financial operations for thousands of Italian SMBs, simplifying cash flow management, e-invoicing, and payment scheduling. Developed and optimised backend infrastructure in Elixir, ensuring robustness, scalability, and reliability of Sibill's core platform. Leveraged AI and integrated large language models (LLMs) directly into the product to automate workflows and deliver smarter, more intuitive user experiences.\\
       \texttt{Elixir}\slashsep\texttt{TypeScript}\slashsep\texttt{AWS}\slashsep\texttt{LLM}\slashsep\texttt{AI}}

    \entry{02/2024 \newline 05/2024\\\footnotesize{full remote --- short-term engagement}}
        {Senior Backend Engineer}
        {Remote \textnormal{(HR Tech)}}
        {Supported Remote.com's mission to simplify global employment by enabling companies to hire and manage talent across borders. Developed and enhanced backend infrastructure for the expenses product in Elixir, building scalable, reliable, and compliant systems. Streamlined employee expense management workflows for companies operating at a global scale.\\
       \texttt{Elixir}\slashsep\texttt{AWS}}

    \entry{04/2022 \newline 01/2024\\\footnotesize{full remote}}
        {Senior Software Developer}
        {Forza Football \textnormal{(Sports Tech)}}
        {Developed and maintained a high-throughput real-time data ingestion system in Elixir, processing live football match updates from multiple external data providers at scale. Contributed to and maintained several open-source Elixir libraries developed by the company.\\
       \texttt{Elixir}\slashsep\texttt{AWS}\slashsep\texttt{Terraform}}

    \entry{04/2020 \newline 03/2022\\\footnotesize{Milan --- hybrid remote}}
        {Software Developer}
        {Casavo \textnormal{(PropTech)}}
        {Built backend infrastructure and microservices from scratch in Elixir and Rust for a real estate listing platform and an internal transaction management tool. Implemented the core domain using the Commanded library following CQRS and Event Sourcing patterns. Established and evolved Test Automation, CI/CD pipelines, and Observability practices.\\
       \texttt{Elixir}\slashsep\texttt{Rust}\slashsep\texttt{TypeScript}\slashsep\texttt{Python}}

    \entry{06/2018 \newline 03/2020\\\footnotesize{Milan --- full time}}
        {Software Developer}
        {Prima Assicurazioni S.p.A. \textnormal{(InsurTech)}}
        {Developed new features and maintained an insurance back-office platform across a polyglot stack including Elixir, PHP, Elm, and Haskell. Improved system reliability and code quality through active refactoring and adherence to engineering best practices.\\
       \texttt{Elixir}\slashsep\texttt{PHP}\slashsep\texttt{Elm}\slashsep\texttt{Haskell}}

    \entry{09/2016 \newline 05/2018\\\footnotesize{Milan --- full time}}
        {Software Developer}
        {Deus Technology \textnormal{(FinTech)}}
        {Implemented new features and maintained a performance-critical financial back-office platform in Python and Java. Designed and built an intraday financial market data collection system, aggregating feeds from multiple external data providers.\\
       \texttt{Python}\slashsep\texttt{Java}\slashsep\texttt{Bash}\slashsep\texttt{C}}

    \entry{01/2016 \newline 08/2016\\\footnotesize{Milan --- contract}}
        {Software Developer}
        {ECRM Italia \textnormal{(MarTech)}}
        {Analyzed, designed, and developed a digital rewards and gifting platform using Microsoft technologies (C\#, .NET). Provided on-site technical consulting at ABB Automation.\\
       \texttt{C\#}\slashsep\texttt{.NET}\slashsep\texttt{JavaScript}}

    \entry{04/2015 \newline 01/2016\\\footnotesize{Milan/Bologna --- full time}}
        {.NET Developer / Consultant}
        {YOOX Group \textnormal{(Fashion E-commerce)}}
        {Designed and developed RESTful APIs for the internal orders team using ASP.NET Web API, a messaging system with RabbitMQ, and MongoDB. Led the migration to a new IBM inventory and e-commerce system in Java and Scala. Served as tech lead for the lost-and-returns, payment, and fraud detection teams.\\
       \texttt{C\#}\slashsep\texttt{.NET}\slashsep\texttt{Java}\slashsep\texttt{Scala}\slashsep\texttt{JavaScript}}

    \entry{03/2012 \newline 03/2015\\\footnotesize{Milan --- full time}}
        {Software Developer / Architect}
        {Dev4Side \textnormal{(Software Consultancy)}}
        {Developed web applications using ASP.NET and various JavaScript frameworks. Built cross-platform mobile applications for iOS, Android, and Windows Phone using Xamarin and native languages (Objective-C, Java, C\#). Designed and developed a web-based application using Node.js and Meteor.js. Speaker at industry events and meetups.\\
       \texttt{C\#}\slashsep\texttt{.NET}\slashsep\texttt{Xamarin}\slashsep\texttt{Node.js}\slashsep\texttt{JavaScript}}

    \entry{05/2011 \newline 02/2012\\\footnotesize{Padova --- full time}}
        {Junior Software Developer}
        {Sia-Net S.r.l. \textnormal{(Web Agency)}}
        {Designed and developed websites and web applications in C\# using ASP.NET (WebForms and MVC), deployed on both Windows and Linux (Mono) environments.\\
     \texttt{C\#}\slashsep\texttt{.NET}\slashsep\texttt{JavaScript}\slashsep\texttt{Mono}}

     \entry{11/2008 \newline 04/2011\\\footnotesize{Treviso --- full time}}
        {Junior Software Developer}
        {Ergon Informatica \textnormal{(IT Consultancy)}}
        {Analyzed business requirements and developed customized ERP software applications covering sales, production, purchasing, planning, inventory management, and management control. Built small web and mobile applications, managed virtual infrastructure (VMware), and provided Help Desk and technical support.\\
       \texttt{VB6}\slashsep\texttt{VB.NET}\slashsep\texttt{.NET}\slashsep\texttt{C}}

    \entry{04/2004 \newline 10/2008\\\footnotesize{Padova --- full time}}
        {PLC Manager --- Industrial machine division}
        {Digipack S.r.l. \textnormal{(Industrial Automation)}}
        {Automated industrial processes and programmed anthropomorphic robots (ABB, FANUC, KUKA) for product movement and handling. Applied FANUC TP/KAREL, ABB RAPID, KUKA KRL, and Siemens PLC languages (KOP, FUP, AWL). Conducted R\&D for new industrial automation solutions.\\
       \texttt{C}\slashsep\texttt{VB.NET}\slashsep\texttt{Assembly}}

\end{entrylist}

%----------------------------------------------------------------------------------------
% education
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
    \entry{1999 \newline 2004\\\footnotesize{Treviso}}
        {Electrical and Advanced Industrial Automation --- 100/100}
        {Istituto Tecnico Industriale "E.Barsanti"}
        {}
\end{entrylist}

%----------------------------------------------------------------------------------------
% certifications
%----------------------------------------------------------------------------------------

\cvsect{Certifications}

\begin{entrylist}

    \entry{2021\\\footnotesize{Online}}
        {Decision-making for Software Development Teams Workshop}
        {Avanscoperta}
        {ID\@: 2021 07 01}
    \entry{2021\\\footnotesize{Online}}
        {Applied Functional Programming Workshop}
        {Avanscoperta}
        {ID\@: 2021 06 23}
    \entry{2021\\\footnotesize{Online}}
        {EventStorming Remote Modelling Workshop}
        {Avanscoperta}
        {ID\@: 2021 05 11}
    \entry{2021\\\footnotesize{Online}}
        {Haskell Fundamentals}
        {47 Degrees}
        {}
    \entry{2022\\\footnotesize{Online}}
        {Microservices Practical Workshop}
        {Avanscoperta}
        {ID\@: 2022 01 21}
\end{entrylist}

%----------------------------------------------------------------------------------------
% other activities
%----------------------------------------------------------------------------------------

\cvsect{Other Activities}

\begin{entrylist}
    \entry{2019 \newline Present\\\footnotesize{Worldwide}}
        {Autonomous \& Self-Driving Robots}
        {Personal Project}
        {Designing and building autonomous and self-driving robots as a personal passion project. Lego Robot Champion --- competed and won in international Lego robotics competitions.\\
       \texttt{Robotics}\slashsep\texttt{Autonomous Systems}\slashsep\texttt{Embedded C}}
\end{entrylist}

%----------------------------------------------------------------------------------------
% additional information
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
    \vspace{-\baselineskip}

    \cvsect{Languages}

    \textbf{Italian} --- native\\
    \textbf{English} --- proficient\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
    \vspace{-\baselineskip}

    \cvsect{Hobbies}

    Tech speaking, blogging, running, and participating in various meetups and user groups.
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
    \vspace{-\baselineskip}

    \cvsect{Open Source}

    Actively contributing to open-source projects on GitHub.
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
```

Now let me rebuild the PDF:
